\documentclass[margin,15pt]{res} % default is 10 pt
% margin option puts section titles to left of text
%\usepackage{helvetica} % uses helvetica postscript font (download helvetica.sty)
%\usepackage{newcent}   % uses new century schoolbook postscript font 
\usepackage[usenames,dvipsnames]{xcolor}
\usepackage{hyperref} 
\hypersetup{
    colorlinks=false,
    urlbordercolor=Blue,
    pdfborderstyle={/S/U/W 1},
}

\newcommand{\gli}[2] {
  {\color{Blue} \href{#1}{#2}}
}

\newcommand{\wsum}[3] {
\begin{tabular}{ r l }
\bf Project: & #1 \\
\bf Role: & #2 \\
\bf Duration: & #3  \\
\end{tabular}
}
\begin{document}
\name{Arkadii Galiash\\[12pt]} % the \\[12pt] adds a blank line after name

\address{{\bf Contacts} \\  Saint Petersburg, Russia \\
        \gli{mailto:arkady.galyash@gmail.com?subject=Zalando Job}{arkady.galyash@gmail.com} \\
        +7(921) 553-9890 }
\address{}
\begin{resume}
 
\section{SUMMARY}
  \begin{itemize}
    \item Sun Certified Java Programmer 
    \item Over 5 years of Java GUI development of trading platforms using Swing
    \item Strong in object-oriented design
    \item Extensive experience in BDD (Behaviour-Driven Development) using Cucumber and JBehave
    \item Good knowledge of JavaScript, Perl and UNIX shells
  \end{itemize}
\section{PROFESSIONAL SKILLS} 
  \begin{itemize}
     \item Programming languages: Java SE, shells, Perl, JavaScript
%     \item Lexer/parser generators: JavaCC, bison(YACC), ANTLR, SableCC, lex
     \item VCS: CVS, SVN, git
     \item Tools: vim, IntelliJ IDEA (plugins development), Apache Ant, Maven, Atlassian JIRA, TeamCity
     \item Testing tools: JUnit, JBehave, Cucumber
     \item Other: Unix utilities, XML, HTML, XUL
  \end{itemize}

\section{WORK EXPERIENCE} 

{\bf \gli{http://www.devexperts.com/en/index.html}{Devexperts}, St. Petersburg, Russia} \\
\wsum{Tradable Chart Module}{Senior Java Developer}{Jun/12-present}

Design and develop chart component for standalone Java trading platform, implement technical analysis indicators. \\
Used technologies and tools: Java 7, IntelliJ IDEA, Maven, Spring, SVN, JUnit, \\ JBehave, Atlassian JIRA, TeamCity. \\ \\
\wsum{ThinkOrSwim Chart Module}{Java Developer}{Sep/07-May/12}

  Designed and developed specific scripting programming language (\gli{http://team.thinkorswim.com/manual/dark/thinkscript/index.html}{ThinkScript}) for stock market traders. Also developed GUI on Swing, wrote unit and integration tests, SVN hooks. \\ 
Used technologies and tools: Java, JavaCC, ObjectWeb ASM, IntelliJ IDEA, Apache Ant, CVS, SVN, JUnit, Atlassian JIRA, TeamCity.

{\bf \gli{http://niimm.spbu.ru/tambur_eng.htm}{Smirnov Scientific Research Institute in Mathematics and Mechanics}, \\ \gli{http://spbu.ru/}{St. Petersburg State University}} \\
\wsum{Make2NetBeans}{Junior Java Developer}{Dec/06-Apr/07}

Developed NetBeans plugin (\gli{http://plugins.netbeans.org/PluginPortal/faces/PluginDetailPage.jsp?pluginid=1495}{Make2NetBeans}) for conversion of GNU make-based projects to NetBeans projects. \\ 
Used technologies and tools: Java, ANTLR.

\section{EDUCATION}       2004-2009 \\ 
                Master degree, Computer Science department  \\
                \gli{http://www.math.spbu.ru/en/index.html}{The Faculty of Mathematics And Mechanics} \\
		\gli{http://spbu.ru/}{St. Petersburg State University} \\
 
 
\section{CERTIFICATES}
2008 - Sun Certified Programmer for the Java Platform, SE 6 \\
2007 - Sun Certified Programmer for the Java Platform, SE 5 \\

\section{OPEN SOURCE} \gli{https://github.com/gark87}{github account} \\
    \gli{http://sourceforge.net/users/gark87}{sourceforge account}
\end{resume} 
\end{document}
