\documentclass[margin,15pt]{res} % default is 10 pt
% margin option puts section titles to left of text
%\usepackage{helvetica} % uses helvetica postscript font (download helvetica.sty)
%\usepackage{newcent}   % uses new century schoolbook postscript font 
\usepackage[usenames,dvipsnames]{xcolor}
\usepackage{hyperref} 
\hypersetup{
    colorlinks=false,
    urlbordercolor=Blue,
    pdfborderstyle={/S/U/W 1},
}

\newcommand{\gli}[2] {
  {\color{Blue} \href{#1}{#2}}
}

\newcommand{\wsum}[3] {
\begin{tabular}{ r l }
\bf Project: & #1 \\
\bf Role: & #2 \\
\bf Duration: & #3  \\
\end{tabular}
}
\newcommand{\gh}[3] {
\begin{tabular}{ r l }
\bf Project: & \gli{https://github.com/gark87/#1}{#2} \\
\bf Technology: & #3 \\
\end{tabular} \\
}

\begin{document}
\name{Arkadii Galiash\\[12pt]} % the \\[12pt] adds a blank line after name

\address{{\bf Contacts} \\  Saint Petersburg, Russia \\
        \gli{mailto:arkady.galyash@gmail.com?subject=Job}{arkady.galyash@gmail.com} \\
        +7(921) 553-9890 }
\address{}
\begin{resume}
 
\section{SUMMARY}
  \begin{itemize}
    \item Sun Certified Java Programmer 
    \item Over 6 years of Java GUI development of trading platforms using Swing
    \item Strong in object-oriented design
    \item Extensive experience in BDD (Behaviour-Driven Development) using Cucumber and JBehave
    \item Good knowledge of JavaScript, Perl and UNIX tools
  \end{itemize}
\section{PROFESSIONAL SKILLS} 
  \begin{itemize}
     \item Programming languages: Java SE, shells, Perl, JavaScript, Scala
     \item Lexer/parser generators: JavaCC, bison(YACC), ANTLR, SableCC, lex
     \item VCS: CVS, SVN, git
     \item Tools: vim, IntelliJ IDEA (plugins development), Apache Ant, Maven, Ivy, Atlassian JIRA
     \item CI: TeamCity, Hudson, Travis
     \item Testing tools: JUnit, JBehave, Cucumber
     \item Other: Unix utilities, XML, HTML, XUL
  \end{itemize}

\section{WORK EXPERIENCE} 

{\bf \gli{http://www.devexperts.com/en/index.html}{Devexperts}, St. Petersburg, Russia} \\
\wsum{Tradable Chart Module}{Senior Java Developer}{Jun/12-present}

Design and develop chart component (both client and server side) for standalone Java trading platform, implement technical analysis indicators. 

{\bf Responsibilities:} 
\begin{itemize}
  \item New features development
  \item Design and planning of the code architecture
  \item Development times estimation
  \item Continious Integration support
  \item Code review
  \item Mentoring
\end{itemize}

{\bf Key achivements: }
\begin{itemize}
  \item To improve quality and reduce costs I implemented integration tests using JBehave. Now when QA finds a bug they just describe S2R as user story and it can be used as test.
  \item Because we needed chart module in our Android application too, I've added additional painting layer to separate model, controller and even view from Swing framework.
\end{itemize}
Used technologies and tools: Java 7, IntelliJ IDEA, Maven, Spring, SVN, JUnit, \\ JBehave, Atlassian JIRA, TeamCity. \\ \\
\wsum{ThinkOrSwim Chart Module}{Java Developer}{Sep/07-May/12}

  I've designed and developed Domain-Specific Language (\gli{http://team.thinkorswim.com/manual/dark/thinkscript/index.html}{ThinkScript}) for traders to calculate custom technical analysis strategies. \\
I wrote:
\begin{itemize} 
\item frontend (parser, internal representation)
\item backend (JVM bytecode generation)
\item runtime (user strategies can be run both on client and server sides)
\item small IDE for this custom language (editor, syntax highlighting, visual editor).
\end{itemize}
 Most interesting was visual editor (Condition Wizard) which allows user to form script by combining of some predefined scripts, options and inputs.
 Also developed GUI on Swing, wrote unit and integration tests, SVN hooks. \\ 
Used technologies and tools: Java, JavaCC, ObjectWeb ASM, IntelliJ IDEA, Apache Ant, CVS, SVN, JUnit, Atlassian JIRA, TeamCity.

{\bf \gli{http://niimm.spbu.ru/tambur_eng.htm}{Smirnov Scientific Research Institute in Mathematics and Mechanics}, \\ \gli{http://spbu.ru/}{St. Petersburg State University}} \\
\wsum{Make2NetBeans}{Junior Java Developer}{Dec/06-Apr/07}

Developed NetBeans plugin (\gli{http://plugins.netbeans.org/PluginPortal/faces/PluginDetailPage.jsp?pluginid=1495}{Make2NetBeans}) for conversion of GNU make-based projects to NetBeans projects. \\ 
Used technologies and tools: Java, ANTLR.

\section{OPEN SOURCE} 
  \gh{ideaCC}{ideaCC}{Java, JavaCC, IntelliJ platform} 
JavaCC (LL(k) parser generator) support (syntax, highlighting, navigation, etc.). 

  \gh{SmartFilters}{SmartFilters}{Javascript, XUL, SQLite} 
I receive enormous amount of e-mail every day and I would like to have automatic filtering system based on several criteria analysis (e.g. theme, address, mailing user agent). \\
I've developed this Thunderbird plugin using JavaScript and XUL. Also I've used unsupervised Machine Learning (k-means clustering) algorithm to find out regularities in emails subjects. 

  \gh{yajom}{yajom}{Scala} 
We needed to transform one JAXB objects to another, we used \gli{http://nomin.sourceforge.net/}{nomin} (Groovy framework with DSL to describe such transformations).\\
Nomin has the following problems: no compile-time checks, weak IDE support, no static typing, weak performance, poor debug support.
I've developed Scala analogue using Scala macroses and implicits without these weaknesses.

  \gh{gark87-GM-scripts}{Greasemonkey scripts}{Javascript, JIRA, Polarion} 
Various scripts to improve everyday working process with JIRA and Polarion.

\section{EDUCATION}       2004-2009 \\ 
                Master degree, Computer Science department  \\
                \gli{http://www.math.spbu.ru/en/index.html}{The Faculty of Mathematics And Mechanics} \\
		\gli{http://spbu.ru/}{St. Petersburg State University} \\
 
 
\section{CERTIFICATES}
2008 - Sun Certified Programmer for the Java Platform, SE 6 \\
2007 - Sun Certified Programmer for the Java Platform, SE 5 \\
\gli{https://www.coursera.org/user/i/abfc0ac6e61ca09d51d659e3b46a0899}{coursera account}
\end{resume} 
\end{document}
